Appendix: A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-23 appendix.Rmd
moved signal strength into expt design section and swapped participant to subject

## Mapping of subjects to experimental factors

Mapping of subjects to experimental factors is an important part of experiment design. Essentially, we want to maximum the difference in factors exposed to a subject. For this purpose, we design an algorithm to conduct subject allocation. Let $L$ be a set of available lineups and $S$ be a set of available subjects. According to the experimental design, the availability of a lineup is associated with the number of subjects it can assign to. For lineups with uniform fitted value distribution, this value is 11. And other lineups can be allocated to at most five different subjects. The availability of a subject is associated with the number of lineups that being allocated to this subject. A subject can view at most 18 different lineups.

The algorithm starts from picking a random subject $s \in S$ with the minimum number of allocated lineups. It then tries to find a lineup $l \in L$ that can maximise the distance metric $D$ and allocate it to subject $s$. Set $L$ and $S$ will be updated and the picking process will be repeated until there is no available lineups or subjects.

Let $F_1,...,F_q$ be $q$ experimental factors, and $f_1, ...,f_q$ be the corresponding factor values. We say $f_i$ exists in $L_{s}$ if any lineup in $L_{s}$ has this factor value. Similarly, $f_if_j$ exists in $L_{s}$ if any lineup in $L_{s}$ has this pair of factor values. And $f_if_jf_k$ exists in $L_{s}$ if any lineup in $L_{s}$ has this trio of factor values. The distance metric $D$ is defined between a lineup $l$ and a set of lineups $L_{s}$ allocated to a subject $s$ if $L_{s}$ is non-empty:

@@

The distance measures how different a lineup is from the set of lineups allocated to the subject in terms of factor values. Thus, the algorithm will try to allocate the most different lineup to a subject at each step.

@@

The survey data is collected via a self-hosted website designed by us. The complete architecture is provided in Figure \ref{fig:tech}. The website is built with the `Flask` [@flask] web framework and hosted on `PythonAnywhere` [@pythonanywhere]. It is configured to handle HTTP requests such that subjects can correctly receive webpages and submit responses. Embedded in the resources sent to subjects, the `jsPsych` front-end framework [@jspsych] instructs subjects' browsers to render an environment for running behavioral experiments. During the experiment, this framework will automatically collect common behavioral data such as response time and clicks on buttons. Subjects' responses are first validated by a scheduled `Python` script run on the server, then push to a Github repository. Lineup images shown to users are saved in multiple Github repositories and hosted in corresponding Github pages. The URLs to these images are resolved by `Flask` and bundled in HTML files.

@@

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  add_row(Pronoun = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Pronoun, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Pronoun", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"), 
                    booktabs = TRUE, 
                    label = "pronoun", 
                    caption = "Summary of pronoun distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(age_group) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Age group` = age_group) %>%
  add_row(`Age group` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Age group`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Age group", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "age-group", 
                    caption = "Summary of age distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  add_row(Education = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Education, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Education", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "education", 
                    caption = "Summary of education distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(previous_experience) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Previous experience` = previous_experience) %>%
  add_row(`Previous experience` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Previous experience`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Previous experience", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "experience", 
                    caption = "Summary of previous experience distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

>>>>

## Mapping of participants to experimental factors

Mapping of participants to experimental factors is an important part of experiment design. Essentially, we want to maximum the difference in factors exposed to a participant. For this purpose, we design an algorithm to conduct participant allocation. Let $L$ be a set of available lineups and $S$ be a set of available participants. According to the experimental design, the availability of a lineup is associated with the number of participants it can assign to. For lineups with uniform fitted value distribution, this value is 11. And other lineups can be allocated to at most five different participants. The availability of a participant is associated with the number of lineups that being allocated to this participant. A participant can view at most 18 different lineups.

The algorithm starts from picking a random participant $s \in S$ with the minimum number of allocated lineups. It then tries to find a lineup $l \in L$ that can maximise the distance metric $D$ and allocate it to participant $s$. Set $L$ and $S$ will be updated and the picking process will be repeated until there is no available lineups or participants.

Let $F_1,...,F_q$ be $q$ experimental factors, and $f_1, ...,f_q$ be the corresponding factor values. We say $f_i$ exists in $L_{s}$ if any lineup in $L_{s}$ has this factor value. Similarly, $f_if_j$ exists in $L_{s}$ if any lineup in $L_{s}$ has this pair of factor values. And $f_if_jf_k$ exists in $L_{s}$ if any lineup in $L_{s}$ has this trio of factor values. The distance metric $D$ is defined between a lineup $l$ and a set of lineups $L_{s}$ allocated to a participant $s$ if $L_{s}$ is non-empty:

@@

The distance measures how different a lineup is from the set of lineups allocated to the participant in terms of factor values. Thus, the algorithm will try to allocate the most different lineup to a participant at each step.

@@

The survey data is collected via a self-hosted website designed by us. The complete architecture is provided in Figure \ref{fig:tech}. The website is built with the `Flask` [@flask] web framework and hosted on `PythonAnywhere` [@pythonanywhere]. It is configured to handle HTTP requests such that participants can correctly receive webpages and submit responses. Embedded in the resources sent to participants, the `jsPsych` front-end framework [@jspsych] instructs participants' browsers to render an environment for running behavioral experiments. During the experiment, this framework will automatically collect common behavioral data such as response time and clicks on buttons. participants' responses are first validated by a scheduled `Python` script run on the server, then push to a Github repository. Lineup images shown to users are saved in multiple Github repositories and hosted in corresponding Github pages. The URLs to these images are resolved by `Flask` and bundled in HTML files.

@@

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  add_row(Pronoun = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Pronoun, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Pronoun", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"), 
                    booktabs = TRUE, 
                    label = "pronoun", 
                    caption = "Summary of pronoun distribution of participants recruited in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(age_group) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Age group` = age_group) %>%
  add_row(`Age group` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Age group`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Age group", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "age-group", 
                    caption = "Summary of age distribution of participants recruited in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  add_row(Education = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Education, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Education", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "education", 
                    caption = "Summary of education distribution of participants recruited in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(previous_experience) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Previous experience` = previous_experience) %>%
  add_row(`Previous experience` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Previous experience`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Previous experience", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "experience", 
                    caption = "Summary of previous experience distribution of participants recruited in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

### 2023-04-23 appendix.tex
moved signal strength into expt design section and swapped participant to subject

\hypertarget{mapping-of-subjects-to-experimental-factors}{%
\subsection{Mapping of subjects to experimental
factors}\label{mapping-of-subjects-to-experimental-factors}}

Mapping of subjects to experimental factors is an important part of
experiment design. Essentially, we want to maximum the difference in
factors exposed to a subject. For this purpose, we design an algorithm
to conduct subject allocation. Let \(L\) be a set of available lineups
and \(S\) be a set of available subjects. According to the experimental
design, the availability of a lineup is associated with the number of
subjects it can assign to. For lineups with uniform fitted value
distribution, this value is 11. And other lineups can be allocated to at
most five different subjects. The availability of a subject is
associated with the number of lineups that being allocated to this
subject. A subject can view at most 18 different lineups.

The algorithm starts from picking a random subject \(s \in S\) with the
minimum number of allocated lineups. It then tries to find a lineup
\(l \in L\) that can maximise the distance metric \(D\) and allocate it
to subject \(s\). Set \(L\) and \(S\) will be updated and the picking
process will be repeated until there is no available lineups or
subjects.

Let \(F_1,...,F_q\) be \(q\) experimental factors, and \(f_1, ...,f_q\)
be the corresponding factor values. We say \(f_i\) exists in \(L_{s}\)
if any lineup in \(L_{s}\) has this factor value. Similarly, \(f_if_j\)
exists in \(L_{s}\) if any lineup in \(L_{s}\) has this pair of factor
values. And \(f_if_jf_k\) exists in \(L_{s}\) if any lineup in \(L_{s}\)
has this trio of factor values. The distance metric \(D\) is defined
between a lineup \(l\) and a set of lineups \(L_{s}\) allocated to a
subject \(s\) if \(L_{s}\) is non-empty:

@@

The survey data is collected via a self-hosted website designed by us.
The complete architecture is provided in Figure \ref{fig:tech}. The
website is built with the \texttt{Flask} \citep{flask} web framework and
hosted on \texttt{PythonAnywhere} \citep{pythonanywhere}. It is
configured to handle HTTP requests such that subjects can correctly
receive webpages and submit responses. Embedded in the resources sent to
subjects, the \texttt{jsPsych} front-end framework \citep{jspsych}
instructs subjects' browsers to render an environment for running
behavioral experiments. During the experiment, this framework will
automatically collect common behavioral data such as response time and
clicks on buttons. Subjects' responses are first validated by a
scheduled \texttt{Python} script run on the server, then push to a
Github repository. Lineup images shown to users are saved in multiple
Github repositories and hosted in corresponding Github pages. The URLs
to these images are resolved by \texttt{Flask} and bundled in HTML
files.

@@

\caption{\label{tab:pronoun}Summary of pronoun distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Pronoun & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
He & 77 & 17.4 & 79 & 17.8 & 61 & 13.8 & 217 & 49.0\\
She & 78 & 17.6 & 77 & 17.4 & 61 & 13.8 & 216 & 48.8\\
Other & 5 & 1.1 & 4 & 0.9 & 1 & 0.2 & 10 & 2.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:age-group}Summary of age distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Age group & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
18-24 & 83 & 18.7 & 86 & 19.4 & 51 & 11.5 & 220 & 49.7\\
25-39 & 69 & 15.6 & 63 & 14.2 & 63 & 14.2 & 195 & 44.0\\
40-54 & 6 & 1.4 & 8 & 1.8 & 6 & 1.4 & 20 & 4.5\\
55-64 & 2 & 0.5 & 3 & 0.7 & 3 & 0.7 & 8 & 1.8\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:education}Summary of education distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Education & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
High School or below & 41 & 9.3 & 53 & 12.0 & 33 & 7.4 & 127 & 28.7\\
Diploma and Bachelor Degree & 92 & 20.8 & 79 & 17.8 & 66 & 14.9 & 237 & 53.5\\
Honours Degree & 6 & 1.4 & 15 & 3.4 & 6 & 1.4 & 27 & 6.1\\
Masters Degree & 21 & 4.7 & 13 & 2.9 & 16 & 3.6 & 50 & 11.3\\
Doctoral Degree & 0 & 0.0 & 0 & 0.0 & 2 & 0.5 & 2 & 0.5\\
\addlinespace
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:experience}Summary of previous experience distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Previous experience & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
No & 96 & 21.7 & 88 & 19.9 & 67 & 15.1 & 251 & 56.7\\
Yes & 64 & 14.4 & 72 & 16.3 & 56 & 12.6 & 192 & 43.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\hypertarget{mapping-of-participants-to-experimental-factors}{%
\subsection{Mapping of participants to experimental
factors}\label{mapping-of-participants-to-experimental-factors}}

Mapping of participants to experimental factors is an important part of
experiment design. Essentially, we want to maximum the difference in
factors exposed to a participant. For this purpose, we design an
algorithm to conduct participant allocation. Let \(L\) be a set of
available lineups and \(S\) be a set of available participants.
According to the experimental design, the availability of a lineup is
associated with the number of participants it can assign to. For lineups
with uniform fitted value distribution, this value is 11. And other
lineups can be allocated to at most five different participants. The
availability of a participant is associated with the number of lineups
that being allocated to this participant. A participant can view at most
18 different lineups.

The algorithm starts from picking a random participant \(s \in S\) with
the minimum number of allocated lineups. It then tries to find a lineup
\(l \in L\) that can maximise the distance metric \(D\) and allocate it
to participant \(s\). Set \(L\) and \(S\) will be updated and the
picking process will be repeated until there is no available lineups or
participants.

Let \(F_1,...,F_q\) be \(q\) experimental factors, and \(f_1, ...,f_q\)
be the corresponding factor values. We say \(f_i\) exists in \(L_{s}\)
if any lineup in \(L_{s}\) has this factor value. Similarly, \(f_if_j\)
exists in \(L_{s}\) if any lineup in \(L_{s}\) has this pair of factor
values. And \(f_if_jf_k\) exists in \(L_{s}\) if any lineup in \(L_{s}\)
has this trio of factor values. The distance metric \(D\) is defined
between a lineup \(l\) and a set of lineups \(L_{s}\) allocated to a
participant \(s\) if \(L_{s}\) is non-empty:

@@

The survey data is collected via a self-hosted website designed by us.
The complete architecture is provided in Figure \ref{fig:tech}. The
website is built with the \texttt{Flask} \citep{flask} web framework and
hosted on \texttt{PythonAnywhere} \citep{pythonanywhere}. It is
configured to handle HTTP requests such that participants can correctly
receive webpages and submit responses. Embedded in the resources sent to
participants, the \texttt{jsPsych} front-end framework \citep{jspsych}
instructs participants' browsers to render an environment for running
behavioral experiments. During the experiment, this framework will
automatically collect common behavioral data such as response time and
clicks on buttons. participants' responses are first validated by a
scheduled \texttt{Python} script run on the server, then push to a
Github repository. Lineup images shown to users are saved in multiple
Github repositories and hosted in corresponding Github pages. The URLs
to these images are resolved by \texttt{Flask} and bundled in HTML
files.

@@

\caption{\label{tab:pronoun}Summary of pronoun distribution of participants recruited in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Pronoun & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
He & 77 & 17.4 & 79 & 17.8 & 61 & 13.8 & 217 & 49.0\\
She & 78 & 17.6 & 77 & 17.4 & 61 & 13.8 & 216 & 48.8\\
Other & 5 & 1.1 & 4 & 0.9 & 1 & 0.2 & 10 & 2.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:age-group}Summary of age distribution of participants recruited in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Age group & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
18-24 & 83 & 18.7 & 86 & 19.4 & 51 & 11.5 & 220 & 49.7\\
25-39 & 69 & 15.6 & 63 & 14.2 & 63 & 14.2 & 195 & 44.0\\
40-54 & 6 & 1.4 & 8 & 1.8 & 6 & 1.4 & 20 & 4.5\\
55-64 & 2 & 0.5 & 3 & 0.7 & 3 & 0.7 & 8 & 1.8\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:education}Summary of education distribution of participants recruited in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Education & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
High School or below & 41 & 9.3 & 53 & 12.0 & 33 & 7.4 & 127 & 28.7\\
Diploma and Bachelor Degree & 92 & 20.8 & 79 & 17.8 & 66 & 14.9 & 237 & 53.5\\
Honours Degree & 6 & 1.4 & 15 & 3.4 & 6 & 1.4 & 27 & 6.1\\
Masters Degree & 21 & 4.7 & 13 & 2.9 & 16 & 3.6 & 50 & 11.3\\
Doctoral Degree & 0 & 0.0 & 0 & 0.0 & 2 & 0.5 & 2 & 0.5\\
\addlinespace
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:experience}Summary of previous experience distribution of participants recruited in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Previous experience & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
No & 96 & 21.7 & 88 & 19.9 & 67 & 15.1 & 251 & 56.7\\
Yes & 64 & 14.4 & 72 & 16.3 & 56 & 12.6 & 192 & 43.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}
